A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-03-08 calculus.tex
typesetting
Shorter version

\begin{table}
  \caption{Derivation rules for one automaton.}\label{tbl:rules:single}
\begin{tabular}{@{}l>{$}c<{$}p{3cm}@{}}\toprule
  Name & \text{Rule} & Side conditions\\
  \midrule

@@

The rules of \Calculus{} for one automaton are given in
\cref{tbl:rules:single}. The rules operate on sets of formulas and can
be interpreted as rules of a one-sided sequent calculus, in which all
formulas are located in the antecedent~\cite{Fitting96a}.
%
The rules relate premises~$\SomeClause_1, \ldots, \SomeClause_k$ with
some conclusion~$\SomeClause$. 
%
When constructing a proof, we start with some root~$\SomeClause$, and
then apply proof rules to the goals of the proof, in bottom-up
direction, until all goals are closed, or no more rule is applicable.

A proof in which all proof goals are closed shows that the formulas
in the root~$\SomeClause$ of the proof are inconsistent, and do not
have any solutions. A proof goal that cannot be closed, but to which no
more rules are applicable, gives rise to  a solution of the formulas in the
root~$\SomeClause$. Such an open proof goal will only contain formulas
in Presburger arithmetic allowing a solution to be computed using
standard algorithms~\cite{DBLP:books/daglib/0022394}.

>>>>

\begin{table}
  \caption{Derivation rules for one automaton.}\label{tbl:rules:single}
\begin{tabular}{l>{$}c<{$}p{3cm}}\toprule
  Name & \text{Rule} & Side conditions\\
  \midrule

@@

The rules of \Calculus{} for one automaton are given in
\cref{tbl:rules:single}. The rules operate on sets of formulas and can
be interpreted as rules of a one-sided sequent calculus, in which all
formulas are located in the antecedent~\cite{Fitting96a}.
%
The rules relate premises~$\SomeClause_1, \ldots, \SomeClause_k$ with
some conclusion~$\SomeClause$. 
%
When constructing a proof, we start with some root~$\SomeClause$, and
then apply proof rules to the goals of the proof in bottom-up
direction until all goals are closed, or no more rules are applicable.

A proof in which all proof goals are closed shows that the formulas
in the root $\SomeClause$ of the proof are inconsistent (have no solutions).
An unclosable goal to which no rules are applicable
gives rise to a solution of the formulas in the
root~$\SomeClause$. Such a goal will only contain formulas
in Presburger arithmetic, allowing a solution to be computed using
standard algorithms~\cite{DBLP:books/daglib/0022394}.

### 2024-03-08 data.tex
Add artefact, update evaluation
Shorter version

A reproduction package featuring all relevant logs and all benchmarked instances is available~\cref{artefact}.
\Catra{} and \Ostrich{} are both available as living software
under a 3-clause BSD~license on GitHub at \url{https://github.com/amandasystems/catra} and \url{https://github.com/uuverifiers/ostrich}
respectively. A version of \Ostrich{} modified to use CA-Str is available in the \texttt{cea-catra}~branch. All source code to generate the paper itself
is available at~\url{https://github.com/amandasystems/oopsla-artefact}.

>>>>

A reproduction package featuring all relevant logs and all benchmarked instances is available~\cite{artefact}.
\Catra{} and \Ostrich{} are both available as living software
under a 3-clause BSD~license on GitHub at \url{https://github.com/amandasystems/catra} and \url{https://github.com/uuverifiers/ostrich}
respectively. A version of \Ostrich{} modified to use CA-Str is available in the \texttt{cea-catra} branch. All source code to generate the paper itself
is available at \url{https://github.com/amandasystems/oopsla-artefact}.
